---
title: "Aides Tests"
author: "Dr K"
date: "May 24, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tigerstats)
require(dplyr)
Genvoyabub <-read.csv(file="Genvoyabub.csv",header=TRUE)
abacavirinol<-read.csv(file="abacavirinol.csv",header=TRUE)
Atriplavast<-read.csv(file="Atriplavast.csv",header=TRUE)
```

#Instructions

Three new preventative aides drugs were tested in clinical trials in 2015. The trial designs were modeled after the famous RV_144 Aides Trials in Tailand in 2009.  Analyze and report on the apparent effectiveness of the three different drugs. Does sex of the participant seem to be a factor for any of the drugs?


# Genvoyabub

We will subset the data by sex to see if the drug is sex specific.


# Atriplavast

We will subset the data by sex to see if the drug is sex specific.

```{r}
Atripla <- xtabs (~infected +group, data=Atriplavast) 
Atripla
```
For group who was infected with <b>AIDS</b>, there were 103 who took Atriplavast, and 131 who took the placebo.

For group who was infected with <b>None</b>, there were 2136 who took Atriplavast, and 2135 who took the placebo.

Lets take a further look into the data.

<b>Infected vs. Group Two-way table: </b>

```{r}
rowPerc(Atripla)
```

For the people who were infected with <b>AIDS</b>, 44.02% took Atriplavast, and 55.59% took the placebo.

For the people who were infected with <b>None</b>, 50.33% took Atriplavast and 49.67% took the placebo.

After reviewing the numerical, people who were infected group with <b>AIDS</b> who took Atriplavast had a lower infection rate than those who took the placebo. The group who was <b>not</b> infected did not show much of a difference. 

Lets look at the groups

<b>Group vs. Infected table: </b>

```{r}
colPerc(Atripla)
```
For the people who took <b>Atriplavast</b>, 4.55% recieved AIDS, and 95.45% recieved none.

For the people who took the <b>placebo</b>, 5.78% recieved AIDS, and 94.22% recieved none.

After reviewing the numerical, people who were infected group with <b>AIDS</b> who took Atriplavast had a lower infection rate than those who took the placebo. The group who was <b>not</b> infected did not show much of a difference. 


Now that we have reviewed the numerical data for, we will construct a bar chart to graphically see the data.

```{r}
barchartGC (Atripla, type="percent")
```

It appears that the people were infected with AIDS have a small difference in the ocuurence of it. The people who took Atriplavast recieved the virus less than those who took the placebo.

```{r}
chisqtestGC(Atripla)
```


##Conclusion

Now for the Femaeles

```{r}
AF<- filter(Atriplavast, sex=="F")
AF2<- xtabs (~infected +group, data=AF)
AF2
```


```{r}
barchartGC (AF2, type="percent")
```


```{r}
chisqtestGC(AF2)
```

##Conclusion

Now for the men
```{r}
AM<- filter (Atriplavast, sex=="M")
AM2<- xtabs (~infected +group, data=AM)
AM2
```


```{r}
barchartGC (AM2, type="percent")
```


```{r}
chisqtestGC(AM2)
```

##Conclusion

# abacavirinol

We will subset the data by sex to see if the drug is sex specific.






