---
title: "Aides Tests"
author: "Dr K"
date: "May 24, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tigerstats)
require(dplyr)
Genvoyabub <-read.csv(file="Genvoyabub.csv",header=TRUE)
abacavirinol<-read.csv(file="abacavirinol.csv",header=TRUE)
Atriplavast<-read.csv(file="Atriplavast.csv",header=TRUE)
```

#Instructions

Three new preventative aides drugs were tested in clinical trials in 2015. The trial designs were modeled after the famous RV_144 Aides Trials in Tailand in 2009.  Analyze and report on the apparent effectiveness of the three different drugs. Does sex of the participant seem to be a factor for any of the drugs?


# Genvoyabub

We will subset the data by sex to see if the drug is sex specific.
```{r}
genovoya <- xtabs (~infected +group, data=Genvoyabub) 
genovoya
```
```{r}
barchartGC (genovoya, type="percent")
```
In this barchart, it does looks like poeple who got AIDS and recieved Genvoyabub have a lowe occurance than those who got AIDS and and recieved the placebo. However, we cannot see a differnece in the group who didnt get AIDS.

```{r}
chisqtestGC(genovoya)
```
The p-value returned from the chi-squared test is 0.5735 which suggests that the probablity of returning a sample similar to this one is about %50 of the time. Since the p-value is higher than 5% we will fail to reject the null hypothesis, therefore there is not a relationship between recieving the vaccine and getting AIDS.


```{r}
GF<- filter(Genvoyabub, sex=="F")
GF2<- xtabs (~infected +group, data=GF)
```

```{r}
barchartGC (GF2, type="percent")
```


```{r}
chisqtestGC(GF2)
```


```{r}
GM<- filter (Genvoyabub, sex=="M")
GM2<- xtabs (~infected +group, data=GM)
```

```{r}
barchartGC(GM2, type="percent")
```


```{r}
chisqtestGC(GM2)
```


# Atriplavast

We will subset the data by sex to see if the drug is sex specific.



# abacavirinol

We will subset the data by sex to see if the drug is sex specific.






